---
title: Process Analysis
author: Mariusz Musiał
mode : selfcontained
framework: revealjs
hitheme : zenburn
revealjs:
  theme: solarized
  transition: convex
  center: "true"
  incremental: "true"
url: {lib: "."}
bootstrap:
  theme: amelia
---
```{r echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(dplyr)

load("assets/procdata.RData") # load the dataframe

procdata <- procdata %>% filter(Process %in% c("A", "B", "C", "D"))
procdata2 <- procdata[sample(nrow(procdata), size = 20, replace = F),]
```

## Process Analysis

<span style="color:green">
*A Developing Data Products Assignment Project*
</span>

---

## Process Analysis App

.fragment to get the overview of statistical parameters

.fragment to transform the data

.fragment to select time range

.fragment to view the distribution and scatterplots

.fragment to test for means equality

.fragment to test for trend change over time

<br>

.fragment <span style="color:green"><small><q>Process Analysis App just does this. It helps to __analyze__ and __compare__ functionally equivalent processes.</q></small></span>

---

## Analyze data in two domains

*** {name: left}
Poulation

```{r, echo=FALSE, class="fragment"}
        ga <- ggplot(procdata, aes(x = Process, y = Performance, fill = Process))
        ga <- ga + geom_violin()
        ga <- ga + geom_boxplot(fill = "grey", color = "red", outlier.colour = "red",
                                outlier.size = 3, width = .2)
        ga <- ga + stat_summary(color = "black", fun.y=mean, geom="point", shape=21, size=4)
        ga <- ga + ggtitle("Process Performance")
        ga <- ga + xlab("Process type")
            ga <- ga + ylab("Performance metric")
        ga <- ga + theme(plot.title = element_text(size = rel(2), 
                                                   colour = "darkblue", face = "bold"))
        ga <- ga + theme(axis.title.y = element_text(size = rel(1.5)))
        ga <- ga + theme(axis.title.x = element_text(size = rel(1.5)))
        ga <- ga + theme(axis.text.x = element_text(size = rel(1.5)))
        ga <- ga + theme(axis.text.y = element_text(size = rel(1.5)))
        ga
```

*** {name: right}
Time

```{r, echo=FALSE, class="fragment"}
    g8 <- ggplot(procdata, aes(x = Date, y = Performance, color = Process))
    g8 <- g8 + geom_point(size = 3, alpha = .6)
    g8 <- g8 + geom_smooth(method = "lm", color = "black")
    g8 <- g8 + facet_wrap(~Process)
    g8 <- g8 + ggtitle("Performance trends per Process Type")
    g8 <- g8 + xlab("Process run date")
    g8 <- g8 + ylab("Performance metric")
    g8 <- g8 + theme(legend.position="none")
    g8 <- g8 + theme(axis.text.x = element_text(angle = 90))
    g8 <- g8 + theme(plot.title = element_text(size = rel(2), 
                                               colour = "darkblue", face = "bold"))
    g8 <- g8 + theme(axis.title.y = element_text(size = rel(1.5)))
    g8 <- g8 + theme(axis.title.x = element_text(size = rel(1.5)))
    g8 <- g8 + theme(axis.text.x = element_text(size = rel(1.5)))
    g8 <- g8 + theme(axis.text.y = element_text(size = rel(1.5)))

    g8
```

---

## Review some selected statistics in a tabular form

```{r, echo=FALSE, results='asis'}
# Hint from https://github.com/ramnathv/slidify/issues/414
# 
dynamic_table <- DT::datatable(procdata2[,1:4],
                               options = list(autoWidth = FALSE,
                                              searching = TRUE,
                                              paging = TRUE,
                                              info = FALSE,
                                              pageLength = 5,
                                              ordering = TRUE)
                               )
DT::saveWidget(dynamic_table, 'example.html')
cat('<iframe src="example.html" STYLE="width:100%" height="400"> </iframe>')
```

<small>The table is live, check it out!</small>

---

## Where to find the stuff?

<ul style="list-style-type:circle">
    <li><a href="https://marioem.shinyapps.io/ProcessAnalysis/">Process Analysis App</a></li>
    <li><a href="https://github.com/marioem/DevelopingDataProducts/tree/master">App code on GitHub</a></li>
    <li><a href="">Presentation code on GitHub</a></li>
</ul>
<br>
<span style="color:green">
*A simple documentation about the app is embedded in the app itself*
</span>

